Instructions for developing new pages for the MarineOmics webpage

### 2023-12-15 DRAFT_DNA_methylation.Rmd
image formatting - meth

```{r,message = FALSE,echo = FALSE}
library(knitr)
knitr::opts_chunk$set(echo = TRUE)
library(knitcitations)
library(kableExtra)
opts_chunk$set(fig.width = 10,
               fig.height = 5,
               cache = FALSE)
cite_options(citation_format = "pandoc", max.names = 3, style = "html", 
             hyperlink = "to.doc")
```

@@

The software used as part of this tutorial is **Bismark Bisulfite Mapper** (@10.1093/bioinformatics/btr167), which is one of the more widely-used softwares to align methylation data to a reference genome. Another commonly-used options include bwa-meth (@pedersen2014fast) and BSMAP (@10.1186/1471-2105-10-232) (see @10.1093/bib/bbab021 and @10.1016/j.csbj.2022.08.051) for comparisons of these software for plant and mammal species, respectively). As with any software it is best to be famililar with the [User Manual](https://felixkrueger.github.io/Bismark/).

Within Bismark, the tutorial uses Bowtie 2 (@10.1038/nmeth.1923) as the alignment software. Although the Bismark user manual covers the necessary Bowtie 2 parameters, it may be useful to refer to the [Bowtie 2 manual](https://bowtie-bio.sourceforge.net/bowtie2/manual.shtml).

@@

```{r meth-ratio, echo = FALSE, out.width = "70%", fig.align = "center"}
knitr::include_graphics("DRAFT_DNA_methylation/meth_ratio.png")
```

*Frequency distribution of methylation ratios for CpG dinucleotides in oyster gill tissue.* @10.7717/peerj.215

```{r meth-igv, echo = FALSE, out.width = "70%", fig.align = "center"}
knitr::include_graphics("DRAFT_DNA_methylation/igv.png")
```

*Screenshot from IGV. Bedgraph files are displayed. See below for code to create these file (File Conversion)*

@@

```{r meth-summary, echo = FALSE, out.width = "70%", fig.align = "center"}
knitr::include_graphics("DRAFT_DNA_methylation/bismark-summary-report.png")
```

>>>>

```{r,message = FALSE,echo = FALSE}
library(knitr)
knitr::opts_chunk$set(echo = TRUE)
library(knitcitations)
library(kableExtra)
opts_chunk$set(fig.width = 10,
               fig.height = 5,
               cache = FALSE)
cite_options(citation_format = "pandoc", max.names = 3, style = "html", hyperlink = "to.html")
```

@@

The software used as part of this tutorial is **Bismark Bisulfite Mapper** [@10.1093/bioinformatics/btr167], which is one of the more widely-used softwares to align methylation data to a reference genome. Another commonly-used options include bwa-meth [@pedersen2014fast] and BSMAP [@10.1186/1471-2105-10-232] (see [@10.1093/bib/bbab021] and [@10.1016/j.csbj.2022.08.051] for comparisons of these software for plant and mammal species, respectively). As with any software it is best to be famililar with the [User Manual](https://felixkrueger.github.io/Bismark/).

Within Bismark, the tutorial uses Bowtie 2 [@10.1038/nmeth.1923] as the alignment software. Although the Bismark user manual covers the necessary Bowtie 2 parameters, it may be useful to refer to the [Bowtie 2 manual](https://bowtie-bio.sourceforge.net/bowtie2/manual.shtml).

@@

```{r meth-ratio, echo = FALSE, out.width = "70%", fig.align = "center", fig.cap = "Frequency distribution of methylation ratios for CpG dinucleotides in oyster gill tissue. @10.7717/peerj.215"}
knitr::include_graphics("DRAFT_DNA_methylation/meth_ratio.png")
```

```{r meth-igv, echo = FALSE, out.width = "100%", fig.align = "center", fig.cap = "Screenshot from IGV. Bedgraph files are displayed. See below for code to create these file (File Conversion)"}
knitr::include_graphics("DRAFT_DNA_methylation/igv.png")
```

---

@@

```{r meth-summary, echo = FALSE, out.width = "100%", fig.align = "center"}
knitr::include_graphics("DRAFT_DNA_methylation/bismark-summary-report.png")
```
